Milestone 7

### 2020-04-29 Draft_1.Rmd
edits to draft

# gg_miss_var(rp_impute, show_pct = TRUE)

@@

aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
title(main = "Patterns of Missingness in the Financial Segregation Data",
      sub = "Is this a caption? qiufwnjekfewkfnwein\nwefjwenmf wiufnwqjenf ewfuiwjnef nfijefnwjenfkqwjnf lqwjefnjqwefjwnef winfjqwhf hjwefwiuefief welfiunqlfjnqkjwe qqfniquwenjfjq iqfnjkjeq rfiunfj q")

>>>>

gg_miss_var(rp_impute, show_pct = TRUE) +
  ggtitle("% Missing Values in Trounstine (2016)'s Racial Polarization Dataset")

nrow(rp_impute)

@@

aggr(fin_imp_aggr, plot = TRUE, bars = TRUE, col=c('navyblue','red'), numbers= FALSE, cex.axis=.5, gap=2, ylab=c("Proporiton of Missing Values","Combinations"))
title(main = "Patterns of Missingness in the Financial Segregation Data",
      sub = "")
